---
title: "Homework 6"
author: Michelle Lui
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(mgcv)
```

### Problem 1
```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

One city
```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Across cities
```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Problem 2

Read in and clean data
```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>%
  na.omit()
```

Plot data: birth weight vs birth length
```{r}
baby_df %>%
  ggplot(aes(x = blength, y = bwt)) +
  geom_point(alpha = .5)
```
I wanted to plot baby's length at birth against baby's birth weight because length was in both of the given models. We see from the graph that there seems to be a relatively linear relationship between birth length and birth weight, hence I will choose to leave it in my proposed model.

Create proposed model
```{r}
my_mod = lm(bwt ~ delwt * wtgain + gaweeks + blength, data = baby_df)
my_mod %>%
  broom::tidy()
```
I created my model based on a hypothesized structure for the factors that underly birth weight. I decided which variables to leave in the model based off of whether or not their estimates were significant when I used broom::tidy. For example, I had originally included malform, but it ended up not being significant (had a p-value greater than 0.05), so I took it out of my model. 

Plot of model residuals against fitted values
```{r}
baby_df %>%
  add_predictions(my_mod) %>%
  add_residuals(my_mod) %>%
  ggplot(aes(x = pred, y = resid)) + geom_point()
```
For the plot of model residuals against fitted values, we see that the residuals mostly center around 0, however at the extreme values we see very large residuals in both the positive and negative direction, showing that this model may not be the best fit for either end of the data, but works for the center of the data. 

Cross validation for all three comparison models
```{r}
cv_df = crossv_mc(baby_df, 100)
cv_df = 
  cv_df  %>%
  mutate(
    twovar_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    threevar_mod = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x)),
    my_mod = map(train, ~lm(bwt ~ delwt * wtgain + gaweeks + blength, data = .x))) %>%
  mutate(
    rmse_twovar = map2_dbl(twovar_mod, test, ~rmse(model = .x, data = .y)),
    rmse_threevar = map2_dbl(threevar_mod, test, ~rmse(model = .x, data = .y)),
    rmse_myvar = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)))
```

plot prediction error distribution
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
When comparing the violin plots for the cross validated prediction error, we get a sense of variance in prediction error and we can compare the prediction error distributions across the different models. It seems that the three way interaction model is the best fit since it has the lowest RMSE, while my model seems slightly better than the birth and gestational age model, but still worse than the three way interaction model. 

### Problem 3

Read in and clean data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Look at parameters for proposed model
```{r}
lm(tmax ~ tmin, data = weather_df) %>%
  broom::tidy() %>%
  knitr::kable(digits = 3)

lm(tmax ~ tmin, data = weather_df) %>%
  broom::glance() %>%
  knitr::kable(digits = 3)
```

*Bootstrap for R squared

produce data frame with estimates
```{r}
bootstrap_rsquared = 
  weather_df %>%
  modelr::bootstrap(n = 50) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) 
```

Plot distribution of R squared estimates
```{r}
bootstrap_rsquared %>%
  ggplot(aes(x = r.squared)) +
  geom_density()
```

Get 95% confidence interval of R squared 
```{r}
bootstrap_rsquared %>%
  summarize(
    ci_lower = quantile(r.squared, 0.025),
    ci_upper = quantile(r.squared, 0.975))
```

*Bootstrap for log(b0 * b1)

produce data frame with estimates
```{r}
bootstrap_log = 
  weather_df %>%
  modelr::bootstrap(n = 50) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>%
  select(.id, term, estimate) %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  )

bootstrap_log =
tibble(
bootstrap_log,
log = log(pull(bootstrap_log, '(Intercept)') * pull(bootstrap_log, tmin)))
```

Plot distribution of log(b0*b1) estimates
```{r}
bootstrap_log %>%
  ggplot(aes(x = log)) +
  geom_density()
```

95% confidence interval of log(b0*b1)
```{r}
bootstrap_log %>%
  summarize(
    ci_lower = quantile(log, 0.025),
    ci_upper = quantile(log, 0.975))
```

